Structured Versus Decorated Cospans

### 2020-12-30 cospans.tex
polished paragraph on Halter-Patterson

Recently Halter and Patterson \cite{HP} implemented this idea in a software tool that lets the user build epidemiological models.  They illustrated the use of their tool by rebuilding part of the COVID-19 model that the UK has been using to make policy decisions.  The advantage of structured (or decorated) cospans is they let one build complex models like this from smaller parts in a mathematically disciplined way, so one can easily add and change parts, and better understand the effect of doing this.

>>>>

Recently Halter and Patterson \cite{HP} implemented this idea in a software tool that makes it easy to build epidemiological models using structured cospans.  They used this to rebuild part of the COVID-19 model that the UK has been using to make policy decisions.  The advantage of using structured or decorated cospans is that one can build complex models from smaller pieces, so one can easily add or change parts, and better understand the effects of doing this.
